UGAN: Improving Underwater Image Quality using Generative Adversarial Networks

### 2017-09-16 files/paper/tex/experiments.tex
update

% I would like this table to match up with the figure showing edge detections. I wasn't able to
% get letters on the left side at each row though.
\begin{table}
\centering
\caption{Distances in image space}
\begin{tabular}{| c | c | c | c |}
   \hline
   Row/Method & CycleGAN & UGAN & UGAN-P \\ \hline
   A          & 116.45 & 85.71  & 86.15  \\ \hline
   B          & 114.49 & 97.92  & 101.01 \\ \hline
   C          & 120.84 & 96.53  & 97.57  \\ \hline
   D          & 129.27 & 108.90 & 110.50 \\ \hline
   Mean       & 111.60 & 94.91  & 96.51 \\ \hline
\end{tabular}
\end{table}

@@

   ~\quad Original & ~CycleGAN & ~\quad UGAN & \quad UGAN-P \\

@@

\begin{table}[ht]
\footnotesize
\centering
\caption{Mean and Standard Deviation Metrics}
\begin{tabular}{| c | c | c | c | c | }
   \hline
   Patch/Method & Original & CycleGAN & UGAN & UGAN-P \\ \hline
   Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline
   Blue & 0.51 $\pm$ 0.18 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 \\ \hline
   Green & 0.36 $\pm$ 0.17 & 0.36 $\pm$ 0.14 & 0.37 $\pm$ 0.17 & 0.36 $\pm$ 0.17 \\ \hline
   Orange & 0.3 $\pm$ 0.15 & 0.25 $\pm$ 0.12 & 0.26 $\pm$ 0.13 & 0.27 $\pm$ 0.14 \\ \hline
\end{tabular}
\end{table}

>>>>

Another metric we can use to compare image patches are the mean and standard deviation of a patch. The standard
deviation gives us a sense of blurriness because it defines how far the data deviates from the mean. A lower standard
deviation means that the data is closer to the mean \starnote{not sure if we exactly need to say that because I assume the reviewers will know what it is}. In the case of images, this would suggest a blurring effect due to the data being
more clustered toward one pixel value. Table \ref{fig:mean_tbl} shows the mean and standard deviations for the local
image patches seen in Figure \ref{fig:zoom}.

% I would like this table to match up with the figure showing edge detections. I wasn't able to
% get letters on the left side at each row though.
\begin{table}
\centering
\caption{Distances in image space}
\begin{tabular}{| c | c | c | c |}
   \hline
   Row/Method & CycleGAN & \textbf{UGAN} & \textbf{UGAN-P} \\ \hline
   A          & 116.45 & 85.71  & 86.15  \\ \hline
   B          & 114.49 & 97.92  & 101.01 \\ \hline
   C          & 120.84 & 96.53  & 97.57  \\ \hline
   D          & 129.27 & 108.90 & 110.50 \\ \hline
   Mean       & 111.60 & 94.91  & 96.51 \\ \hline
\end{tabular}
\end{table}

@@

   ~\quad Original & ~CycleGAN & ~\quad \textbf{UGAN} & \quad \textbf{UGAN-P} \\

@@

\begin{table}[ht]
\footnotesize
\centering
\caption{Mean and Standard Deviation Metrics}
\begin{tabular}{| c | c | c | c | c | }
   \hline
   Patch/Method & Original & CycleGAN & UGAN & UGAN-P \\ \hline
   Red & 0.43 $\pm$ 0.23 & 0.42 $\pm$ 0.22 & 0.44 $\pm$ 0.23 & 0.45 $\pm$ 0.25 \\ \hline
   Blue & 0.51 $\pm$ 0.18 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 & 0.57 $\pm$ 0.17 \\ \hline
   Green & 0.36 $\pm$ 0.17 & 0.36 $\pm$ 0.14 & 0.37 $\pm$ 0.17 & 0.36 $\pm$ 0.17 \\ \hline
   Orange & 0.3 $\pm$ 0.15 & 0.25 $\pm$ 0.12 & 0.26 $\pm$ 0.13 & 0.27 $\pm$ 0.14 \\ \hline
\end{tabular}
\label{fig:mean_tbl}
\end{table}
